### 2021-05-11 proposal/proposal.Rmd
updated proposal

@@

\begin{example}
Let $U_1, ..., U_n \stackrel{iid}{\sim} Uniform(0, 1)$ with order statistics 
$U_{(1)}, ..., U_{(n)}$. Then $\forall a \in (0, 1)$ and $\delta \in (0, 1)$, $\exists N = N(\delta, a) < \infty$ such that $\forall n \geq N$,

@@

Where $N(\delta, a)$ is monotone increasing w.r.t. $\delta$ and $a$. To prove this, we start with the fact that $U_{(i+1)} - U_{(i)} \sim Beta(1, n)$. Then

@@

\begin{equation}
\begin{split}
P(\max_i X_{(i+1)} - X_{(i)} \leq \min_{i, j} \|X_i - Y_j\|) \geq 1 - \delta \\
P(\max_j Y_{(j+1)} - Y_{(j)} \leq \min_{i, j} \|X_i - Y_j\|) \geq 1 - \delta
\end{split}
\end{equation}

for $X_i$ in the first segment and $Y_j$ in the second segment and $X_{(i)}$, $Y_{(j)}$ are order statistics in the first coordinate. If each segment corresponds to a community, this leads to the following two results:

>>>>

In this section, we will consider latent positions sampled uniformly from parallel unit length segments.

\begin{example}
Let $U_1, ..., U_{n_1}, V_1, ..., V_{n_2} \iid Uniform(0, 1)$, $f_1(t) = (t, 0)$, and $f_2(t) = (t, a)$. $X_i = f_1(U_i)$ and $Y_j = f_2(V_j)$ $\forall i \in [n_1]$ and $j \in [n_2]$. If we observe $X_1, ..., X_{n_1}, Y_1, ..., Y_{n_2}$, what approach will allow us to group the observations by segment?
\end{example}

@@

\begin{example}
Let $U_1, ..., U_n \iid Uniform(0, 1)$ with order statistics 
$U_{(1)}, ..., U_{(n)}$. Then $\forall a \in (0, 1)$ and $\delta \in (0, 1)$, $\exists N = N(\delta, a) < \infty$ such that $\forall n \geq N$,

@@

Where $N(\delta, a)$ is monotone increasing with respect to $\delta$ and $a$. To prove this, we start with the fact that $U_{(i+1)} - U_{(i)} \sim Beta(1, n)$. Then

@@

\begin{equation}
P(\max_i X_{(i+1)} - X_{(i)} \leq a \leq \min_{i, j} \|X_i - Y_j\|) 
\geq 1 - \delta / 2
\end{equation}

and similar for $P(\max_j Y_{(j+1)} - Y_{(j)} \leq \min_{i, j} \|X_i - Y_j\|)$, for $X_i$ in the first segment and $Y_j$ in the second segment and $X_{(i)}$, $Y_{(j)}$ are order statistics in the first coordinate. If each segment corresponds to a community, this leads to the following two results:

### 2021-05-11 proposal/proposal.tex
updated proposal

@@

\begin{example}
Let $U_1, ..., U_n \stackrel{iid}{\sim} Uniform(0, 1)$ with order statistics 
$U_{(1)}, ..., U_{(n)}$. Then $\forall a \in (0, 1)$ and $\delta \in (0, 1)$, $\exists N = N(\delta, a) < \infty$ such that $\forall n \geq N$,

@@

\begin{equation}
\begin{split}
P(\max_i X_{(i+1)} - X_{(i)} \leq \min_{i, j} \|X_i - Y_j\|) \geq 1 - \delta \\
P(\max_j Y_{(j+1)} - Y_{(j)} \leq \min_{i, j} \|X_i - Y_j\|) \geq 1 - \delta
\end{split}
\end{equation}

for \(X_i\) in the first segment and \(Y_j\) in the second segment and
\(X_{(i)}\), \(Y_{(j)}\) are order statistics in the first coordinate.
If each segment corresponds to a community, this leads to the following
two results:

>>>>

In this section, we will consider latent positions sampled uniformly
from parallel unit length segments.

\begin{example}
Let $U_1, ..., U_{n_1}, V_1, ..., V_{n_2} \stackrel{\text{iid}}{\sim}Uniform(0, 1)$, $f_1(t) = (t, 0)$, and $f_2(t) = (t, a)$. $X_i = f_1(U_i)$ and $Y_j = f_2(V_j)$ $\forall i \in [n_1]$ and $j \in [n_2]$. If we observe $X_1, ..., X_{n_1}, Y_1, ..., Y_{n_2}$, what approach will allow us to group the observations by segment?
\end{example}

@@

\begin{example}
Let $U_1, ..., U_n \stackrel{\text{iid}}{\sim}Uniform(0, 1)$ with order statistics 
$U_{(1)}, ..., U_{(n)}$. Then $\forall a \in (0, 1)$ and $\delta \in (0, 1)$, $\exists N = N(\delta, a) < \infty$ such that $\forall n \geq N$,

@@

\begin{equation}
P(\max_i X_{(i+1)} - X_{(i)} \leq a \leq \min_{i, j} \|X_i - Y_j\|) 
\geq 1 - \delta / 2
\end{equation}

and similar for
\(P(\max_j Y_{(j+1)} - Y_{(j)} \leq \min_{i, j} \|X_i - Y_j\|)\), for
\(X_i\) in the first segment and \(Y_j\) in the second segment and
\(X_{(i)}\), \(Y_{(j)}\) are order statistics in the first coordinate.
If each segment corresponds to a community, this leads to the following
two results:
